---
title: 'Reproducible Research: Course Project 1'
output: md_document

---

1) Loading of data,preprocessing data, splitting data by date and plotting by 
a histogram of total number of steps taken each day

```{r, echo=TRUE}
data = read.csv('activity.csv')
databydate = split(data,data$date)
Result=sapply(databydate, function(x) sum(x[,1],na.rm=T))
head(Result)
Todataframe = data.frame(Result)
head(Todataframe)
hist(Todataframe$Result, xlab ='Total number of steps per day', main='Histogram')
```

2) Calculating the mean of total number of steps per day
```{r, echo=TRUE}
mean(Todataframe$Result, na.rm=T)
```
3) Calculating the median
```{r,echo=TRUE}
median(Todataframe$Result, na.rm = T)
```

4)Calculating Average daily activity pattern
```{r,echo=TRUE}
ByDate = split(data, data$date)
ByInterval = split(data, data$interval)
Result=sapply(ByInterval, function(x) mean(x[,1],na.rm=T))
data2 = data.frame(Result)
Name = names(Result)
Name2 = as.numeric(as.character(Name))
Name3 = as.data.frame(Name2)
Newdata = cbind(Name3,data2)
colnames(Newdata)[1]= 'Interval'
colnames(Newdata)[2]= 'AvgDailyActivity'
plot(Newdata, xlim=c(0,2500), ylim=c(0,250), type='l')
a = seq(from=0, to = 2500, by = 5)
plot(Newdata, xlim=c(0,2500), ylim=c(0,250), type='l', axes=F)
axis(side=1, at=seq(0,2500,by= 5),labels=a )
axis(side=2, at=seq(0,250,by= 50), labels=c('0','50','100','150','200','250'))
box()
```
5) Find the maximum daily activity
```{r,echo=TRUE}
which.max(Newdata$AvgDailyActivity)
Newdata[104,]
```

6) Find the number of data that has NA values
```{r, echo=TRUE}
colSums(is.na(data))
```

7) Are the difference in activity patterns between weekdays and weekends?
```{r, echo=TRUE}
Ans =mean(data$steps,na.rm=T)
data2 = data
data2$steps[is.na(data2$steps)] = Ans
Byday = split (data2,data2$date)
Result = sapply(Byday, function(x) sum(x[,1]))
Result2 = data.frame(Result)
hist(Result2$Result, col='red', xlab= 'Total number of steps per day', main='Histogram of Total Number of steps per day')
data2$Weekday= weekdays(as.Date(data2$date))
data2$Weekday[(data2$Weekday=='Monday')] = 'weekday'
data2$Weekday[(data2$Weekday=='Tuesday')] = 'weekday'
data2$Weekday[(data2$Weekday=='Wednesday')] = 'weekday'
data2$Weekday[(data2$Weekday=='Thursday')] = 'weekday'
data2$Weekday[(data2$Weekday=='Friday')] = 'weekday'
data2$Weekday[(data2$Weekday=='Saturday')] = 'weekend'
data2$Weekday[(data2$Weekday=='Sunday')] = 'weekend'
data2$Weekday = factor(data2$Weekday)
library(plyr)
Newdata = ddply(data2,c('interval','Weekday'), function(x) apply(x[1],2,mean))
head(Newdata)
library(lattice)
xyplot(steps~interval | Weekday, data= Newdata, layout=c(1,2), type='l')
```
